---
title: "STAT462 S2 Team Tuatara Project"
author: Tingting Guo, Yanxin Hu, Keane Huang, Yiyang Li, Zhonggen Li
output: html_document
date: "2026-08-11"
---

```{=html}
<style>
.boxTask {
background-color: lightblue;
color: black;
border: 2px solid black;
margin: 5px;
padding: 5px;
font-style: italic;
}

.answer {
background-color: #e7f4e4;
border: 2px solid #6f2c87;
}

</style>
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

# un-comment and install following packages if needed
# install.packages("dplyr")
# install.packages("tidyverse")
# install.packages("knitr)
# install.packages("kableExtra")c
# install.packages("sjPlot")
# install.packages("readxl")

# libraries needed for this project
library(dplyr)
# library(tidyverse)
# library(knitr)
library(kableExtra)
# library(sjPlot)
library(readxl)
```

## 1. Data Dictionary

- `CustomerID`: Unique customer ID  
  - `five digit number`  
- `Churn`: Churn Flag  
  - `0`: 
  - `1`:   
- `Tenure`: Tenure of customer in organization  
  - `number`  
  - `NA` 
- `PreferredLoginDevice`: Preferred login device of customer  
  - `Mobile Phone`  
  - `Phone` 
  - `Computer` 
- `CityTier`: City tier  
  - `1`: 
  - `2`: 
  - `3`: 
- `WarehouseToHome`: Distance in between warehouse to home of customer  
  - `number` 
- `PreferredPaymentMode`: Preferred payment method of customer  
  - `Debit Card` 
  - `UPI` 
  - `CC` 
  - `Cash on Delivery` 
  - `E wallet` 
  - `COD` 
  - `Credit Card` 
- `Gender`: Gender of customer  
  - `Female` 
  - `Male` 
- `HourSpendOnApp`: Number of hours spend on mobile application or website 
  - `1`
  - `2` 
  - `3` 
  - `4`
  - `5` 
  - `NA` 
- `NumberOfDeviceRegistered`: Total number of deceives is registered on particular customer  
  - `1` 
  - `2` 
  - `3`
  - `4` 
  - `5` 
  - `6`
- `PreferedOrderCat`: Preferred order category of customer in last month  
  - `Laptop & Accessory` 
  - `Mobile` 
  - `Mobile Phone` 
  - `Others` 
  - `Fashion` 
  - `Grocery` 
- `SatisfactionScore`: Satisfactory score of customer on service  
  - `1` 
  - `2` 
  - `3` 
  - `4`
  - `5`
- `MaritalStatus`: Marital status of customer  
  - `Single` 
  - `Divorced` 
  - `Married` 
- `NumberOfAddress`: Total number of added added on particular customer  
  - `number` 
- `Complain`: Any complaint has been raised in last month  
  - `1` 
  - `0` 
- `OrderAmountHikeFromlastYear`: Percentage increases in order from last year  
  - `number` 
  - `NA` 
- `CouponUsed`: Total number of coupon has been used in last month  
  - `number` 
  - `NA` 
- `OrderCount`: Total number of orders has been places in last month  
  - `number` 
  - `NA` 
- `DaySinceLastOrder`: Day Since last order by customer  
  - `number` 
- `CashbackAmount`: Average cashback in last month  
  - `number` 


## 2. Data Preprocessing and EDA 

Remove all un-related research columns and return a whole related dataset if necessary: 

```{r}

# change xlsx file path to your local relative or absolute path to run
original_data <- read_excel("D:/UC_Courses/STAT462-26S2/group_project/e_commerce/E Commerce Dataset.xlsx", sheet = 2)
str(original_data)

# check all unique values(12) for each column 
lapply(original_data, function(x) head(unique(x), 12))
# remove all un-related columns

# show all column value classes

```

### 2.1 Original Dataset

```{r results='hide'}
kable(head(original_data)) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed")) %>%
  scroll_box(height = "200px", width = "100%")
```

### 2.2 Research Questions Related Dataset

```{r}
# kable(head(related_data)) %>%
#   kable_styling(bootstrap_options = c("striped", "hover", "condensed")) %>%
#   scroll_box(height = "200px", width = "100%")
```

## 3. Research Questions

:::{.boxTask}

#### 3.1 Q1: 

:::

:::{.answer}

#### 3.1.1 Sub-question 1


##### 3.1.1.1 Sub-question 1 Related task 1
__Data Processing if Necessary__

```{r results='hide'}

```

##### 3.1.1.2 Sub-question 1 Related task 2
__Plots__

```{r}

```

##### 3.1.1.3 Sub-question 1 Related task 3
__Findings and Conclusions__

```{r}

```


#### 3.1.2 Sub-question 2


##### 3.1.2.1 Sub-question 2 Related task 1
__Data Processing if Necessary__

```{r results='hide'}

```

##### 3.1.2.2 Sub-question 2 Related task 2
__Plots__

```{r}

```

##### 3.1.2.3 Sub-question 2 Related task 3
__Findings and Conclusions__

```{r}

```

:::

:::{.boxTask}

#### 3.2 Q2: 

:::

:::{.answer}

#### 3.2.1 Sub-question 1


##### 3.2.1.1 Sub-question 1 Related task 1
__Data Processing if Necessary__

```{r results='hide'}

```

##### 3.2.1.2 Sub-question 1 Related task 2
__Plots__

```{r}

```

##### 3.2.1.3 Sub-question 1 Related task 3
__Findings and Conclusions__

```{r}

```


#### 3.2.2 Sub-question 2


##### 3.2.2.1 Sub-question 2 Related task 1
__Data Processing if Necessary__

```{r results='hide'}

```

##### 3.2.2.2 Sub-question 2 Related task 2
__Plots__

```{r}

```

##### 3.2.2.3 Sub-question 2 Related task 3
__Findings and Conclusions__

```{r}

```

:::


:::{.boxTask}

#### 3.3 Q3: 

:::

:::{.answer}

#### 3.3.1 Sub-question 1


##### 3.3.1.1 Sub-question 1 Related task 1
__Data Processing if Necessary__

```{r results='hide'}

```

##### 3.3.1.2 Sub-question 1 Related task 2
__Plots__

```{r}

```

##### 3.3.1.3 Sub-question 1 Related task 3
__Findings and Conclusions__

```{r}

```


#### 3.3.2 Sub-question 2


##### 3.3.2.1 Sub-question 2 Related task 1
__Data Processing if Necessary__

```{r results='hide'}

```

##### 3.3.2.2 Sub-question 2 Related task 2
__Plots__

```{r}

```

##### 3.3.2.3 Sub-question 2 Related task 3
__Findings and Conclusions__

```{r}

```

:::

