---
title: "STAT462 S2 Team Tuatara Project"
author: Tingting Guo, Yanxin Hu, Keane Huang, Yiyang Li, Zhonggen Li
output: html_document
date: "2026-08-11"
---

```{=html}
<style>
.boxTask {
background-color: lightblue;
color: black;
border: 2px solid black;
margin: 5px;
padding: 5px;
font-style: italic;
}

.answer {
background-color: #e7f4e4;
border: 2px solid #6f2c87;
}

</style>
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

# un-comment and install following packages if needed
# install.packages("dplyr")
# install.packages("tidyverse")
# install.packages("knitr)
# install.packages("kableExtra")c
# install.packages("sjPlot")
# install.packages("readxl")

# libraries needed for this project
library(dplyr)
library(tidyverse)
# library(knitr)
library(kableExtra)
# library(sjPlot)
library(readxl)
```

## 1. Data Dictionary (original)

- `CustomerID`: Unique customer ID  
  - `five digit number`  
- `Churn`: Churn Flag  
  - `0`: not churn   
  - `1`: churn 
- *`Tenure`: Tenure of customer in organization  
  - `number`   
  - `NA` 
- *`PreferredLoginDevice`: Preferred login device of customer  
  - `Mobile Phone`  
  - `Phone` - cleaned 
  - `Computer` 
- *`CityTier`:    
  - `1`: Tier 1 City
  - `2`: Tier 2 City 
  - `3`: Tier 3 City
- `WarehouseToHome`: Distance in between warehouse to home of customer  
  - `number` 
  - `NA`
- *`PreferredPaymentMode`: Preferred payment method of customer  
  - `Debit Card` 
  - `UPI` 
  - `CC`: credit card - cleaned  
  - `Cash on Delivery` 
  - `E wallet` 
  - `COD`: cash on delivery - cleaned  
  - `Credit Card` 
- `Gender`: Gender of customer  
  - `Female` 
  - `Male` 
- *`HourSpendOnApp`: Number of hours spend on mobile application or website 
  - `1` 
  - `2` 
  - `3` 
  - `4`
  - `5` 
  - `NA` 
- `NumberOfDeviceRegistered`: Total number of deceives is registered on particular customer  
  - `1` 
  - `2` 
  - `3` 
  - `4` 
  - `5` 
  - `6` 
- *`PreferedOrderCat`: Preferred order category of customer in last month  
  - `Laptop & Accessory` 
  - `Mobile` - cleaned 
  - `Mobile Phone` 
  - `Others` 
  - `Fashion` 
  - `Grocery` 
- `SatisfactionScore`: Satisfactory score of customer on service  
  - `1`: least satisfy 
  - `2` 
  - `3` 
  - `4` 
  - `5`: most satisfy
- `MaritalStatus`: Marital status of customer  
  - `Single` 
  - `Divorced` 
  - `Married` 
- `NumberOfAddress`: Total number of added added on particular customer  
  - `number` 
- `Complain`: Any complaint has been raised in last month
  - `1`: complained  
  - `0`: not complained  
- `OrderAmountHikeFromlastYear`: Percentage increases in order from last year  
  - `number` 
  - `NA` 
- `CouponUsed`: Total number of coupon has been used in last month  
  - `number` 
  - `NA` 
- `OrderCount`: Total number of orders has been places in last month  
  - `number` 
  - `NA` 
- `DaySinceLastOrder`: Day Since last order by customer  
  - `number` 
  - `NA`
- `CashbackAmount`: Average cashback in last month  
  - `number` 


## 2. Data Preprocessing and EDA 

Remove all un-related research columns and return a whole related dataset if necessary: 

```{r}

# change xlsx file path to your local relative or absolute path to run
original_data <- read_excel("D:/UC_Courses/STAT462-26S2/group_project/e_commerce/E Commerce Dataset.xlsx", sheet = 2)
str(original_data)

# check all unique values(12) for each column 
lapply(original_data, function(x) head(unique(x), 20))

```

### 2.1 Original Dataset

```{r}
kable(head(original_data)) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed")) %>%
  scroll_box(height = "200px", width = "100%")
```

### 2.2 Research Questions Related Cleaned Dataset

```{r}
# remove all un-related columns
# TODO: 

# TODO: adjust the NA value replacement methods depending on your research question
# Feature columns cleaning 
summary(original_data$Tenure)

cleaned_data <- original_data %>% 
  # replace Tenure NA value with 0
  mutate(Tenure = replace_na(Tenure, 0)) %>% 
  # change the duplicate values of "PreferredPaymentMode
  mutate(PreferredPaymentMode = recode(PreferredPaymentMode, 
                                       "CC" = "Credit Card", 
                                       "COD" = "Cash on Delivery")) %>% 
  # use median value to replace NA value for WarehouseToHome
  mutate(WarehouseToHome = replace_na(WarehouseToHome, 
                                    median(WarehouseToHome, na.rm = TRUE))) %>% 
  # change the duplicate values of PreferredLoginDevice 
  mutate(PreferredLoginDevice = recode(PreferredLoginDevice, 
                                       "Phone" = "Mobile Phone")) %>% 
  # use median value to replace NA value for HourSPendOnApp
  mutate(HourSpendOnApp = replace_na(HourSpendOnApp, 
                                     median(HourSpendOnApp, na.rm = TRUE))) %>% 
  # change the duplicate values of PreferedOrderCat 
  mutate(PreferedOrderCat = recode(PreferedOrderCat, 
                                   "Moblie" = "Mobile Phone")) %>% 
  # use median value to replace NA value for OrderAmountHikeFromlastYear
  mutate(OrderAmountHikeFromlastYear = replace_na(OrderAmountHikeFromlastYear, 
                        median(OrderAmountHikeFromlastYear, na.rm = TRUE))) %>% 
  # use median value to replace NA value for CouponUsed
  mutate(CouponUsed = replace_na(CouponUsed, median(CouponUsed, 
                                                    na.rm = TRUE))) %>% 
  # use median value to replace NA value for OrderCount
  mutate(OrderCount = replace_na(OrderCount, median(OrderCount, 
                                                    na.rm = TRUE))) %>% 
  # use median value to replace NA value for DaySinceLastOrder
  mutate(DaySinceLastOrder = replace_na(DaySinceLastOrder,
                                        median(DaySinceLastOrder, 
                                               na.rm = TRUE)))

```

```{r}
# show the cleaned data table 
kable(head(cleaned_data)) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed")) %>%
  scroll_box(height = "200px", width = "100%")
```

## 3. Research Questions

:::{.boxTask}

#### 3.1 Q1: 

:::

:::{.answer}

#### 3.1.1 Sub-question 1


##### 3.1.1.1 Sub-question 1 Related task 1
__Data Processing if Necessary__

```{r results='hide'}

```

##### 3.1.1.2 Sub-question 1 Related task 2
__Plots__

```{r}

```

##### 3.1.1.3 Sub-question 1 Related task 3
__Findings and Conclusions__

```{r}

```


#### 3.1.2 Sub-question 2


##### 3.1.2.1 Sub-question 2 Related task 1
__Data Processing if Necessary__

```{r results='hide'}

```

##### 3.1.2.2 Sub-question 2 Related task 2
__Plots__

```{r}

```

##### 3.1.2.3 Sub-question 2 Related task 3
__Findings and Conclusions__

```{r}

```

:::

:::{.boxTask}

#### 3.2 Q2: 

:::

:::{.answer}

#### 3.2.1 Sub-question 1


##### 3.2.1.1 Sub-question 1 Related task 1
__Data Processing if Necessary__

```{r results='hide'}

```

##### 3.2.1.2 Sub-question 1 Related task 2
__Plots__

```{r}

```

##### 3.2.1.3 Sub-question 1 Related task 3
__Findings and Conclusions__

```{r}

```


#### 3.2.2 Sub-question 2


##### 3.2.2.1 Sub-question 2 Related task 1
__Data Processing if Necessary__

```{r results='hide'}

```

##### 3.2.2.2 Sub-question 2 Related task 2
__Plots__

```{r}

```

##### 3.2.2.3 Sub-question 2 Related task 3
__Findings and Conclusions__

```{r}

```

:::


:::{.boxTask}

#### 3.3 Q3: 

:::

:::{.answer}

#### 3.3.1 Sub-question 1


##### 3.3.1.1 Sub-question 1 Related task 1
__Data Processing if Necessary__

```{r results='hide'}

```

##### 3.3.1.2 Sub-question 1 Related task 2
__Plots__

```{r}

```

##### 3.3.1.3 Sub-question 1 Related task 3
__Findings and Conclusions__

```{r}

```


#### 3.3.2 Sub-question 2


##### 3.3.2.1 Sub-question 2 Related task 1
__Data Processing if Necessary__

```{r results='hide'}

```

##### 3.3.2.2 Sub-question 2 Related task 2
__Plots__

```{r}

```

##### 3.3.2.3 Sub-question 2 Related task 3
__Findings and Conclusions__

```{r}

```

:::

:::{.boxTask}

#### 3.4 Q4: 

:::

:::{.answer}

#### 3.4.1 Sub-question 1


##### 3.4.1.1 Sub-question 1 Related task 1
__Data Processing if Necessary__

```{r results='hide'}

```

##### 3.4.1.2 Sub-question 1 Related task 2
__Plots__

```{r}

```

##### 3.4.1.3 Sub-question 1 Related task 3
__Findings and Conclusions__

```{r}

```


#### 3.4.2 Sub-question 2


##### 3.4.2.1 Sub-question 2 Related task 1
__Data Processing if Necessary__

```{r results='hide'}

```

##### 3.4.2.2 Sub-question 2 Related task 2
__Plots__

```{r}

```

##### 3.4.2.3 Sub-question 2 Related task 3
__Findings and Conclusions__

```{r}

```

:::

:::{.boxTask}

#### 3.5 Q5: 

:::

:::{.answer}

#### 3.5.1 Sub-question 1


##### 3.5.1.1 Sub-question 1 Related task 1
__Data Processing if Necessary__

```{r results='hide'}

```

##### 3.5.1.2 Sub-question 1 Related task 2
__Plots__

```{r}

```

##### 3.5.1.3 Sub-question 1 Related task 3
__Findings and Conclusions__

```{r}

```


#### 3.5.2 Sub-question 2


##### 3.5.2.1 Sub-question 2 Related task 1
__Data Processing if Necessary__

```{r results='hide'}

```

##### 3.5.2.2 Sub-question 2 Related task 2
__Plots__

```{r}

```

##### 3.5.2.3 Sub-question 2 Related task 3
__Findings and Conclusions__

```{r}

```

:::